\bf\mftitle

### 2011-03-02 doc/jInfer/xsdimport/xsdimport.tex
"others are skipped"

Enumeration of tag attributes currently recognized by our parsers. They are the following.
\begin{itemize}
	\item \code{name}
	\item \code{ref}
	\item \code{type}
	\item \code{use}
	\item \code{minOccurs}
	\item \code{maxOccurs}
\end{itemize}
List should be extended according to the parser, to reflect its functionality.

@@

Enumeration of tags currently known by our parsers. They are the following.
\begin{itemize}
	\item \code{schema}
	\item \code{element}
	\item \code{complexType}
	\item \code{sequence}
	\item \code{choice}
	\item \code{all}
	\item \code{attribute}
	\item \code{redefine} - this tag is not yet supported, but allows parsing of a certain types of documents
\end{itemize}
This list should also be updated in case the parser functionality is extended.

@@

The modular design of the parser implementations is also an example of extensibility which can be achieved using the NetBeans platform. It allows developers to add, or remove, custom parsers just by creating a module with a new parser implementation; there is no need to change any code within \code{XSDImporter} module. Only exception is the re-definition of the default parser (currently DOM), which is not needed even if the module of default parser is not present.\\
Parsers with extended or custom functionality can be created using \code{XSDImportDOM} module as example (recomended).

>>>>

Enumeration of tag attributes currently recognized by our parsers. Others are simply skipped. They are the following.
\begin{itemize}
	\item \code{name}
	\item \code{ref}
	\item \code{type}
	\item \code{use}
	\item \code{minOccurs}
	\item \code{maxOccurs}
\end{itemize}
List should be extended according to the parser, to reflect its functionality.

@@

Enumeration of tags currently known by our parsers. Others are simply skipped. They are the following.
\begin{itemize}
	\item \code{schema}
	\item \code{element}
	\item \code{complexType}
	\item \code{sequence}
	\item \code{choice}
	\item \code{all}
	\item \code{attribute}
	\item \code{redefine} - this tag is not yet supported, but allows parsing of a certain types of documents
\end{itemize}
This list should also be updated in case the parser functionality is extended.

@@

The modular design of the parser implementations is also an example of extensibility which can be achieved using the NetBeans platform. It allows developers to add, or remove, custom parsers just by creating a module with a new parser implementation; there is no need to change any code within \code{XSDImporter} module. Only exception is the re-definition of the default parser (currently DOM), which is not needed even if the module of default parser is not present.

Parsers with extended or custom functionality can be created using \code{XSDImportDOM} module as example (recomended).
